---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# inferRecom

<!-- badges: start -->
<!-- badges: end -->

inferRecom provides tools for analyzing meiotic recombination events and runs of
homozygosity in family-based genetic data.

## Installation

```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("inferRecom")
```

## Usage

To detect recombinations from maternal meioses in a family with 3+ children: 

```{r, eval=FALSE}
library(inferRecom)

# Detect crossovers
crossovers <- xoDetect(
  plinkFile = "path/to/data",
  mapFile = "path/to/map.txt",
  familySize = 3,
  parent = "mother"
)
```

## Vignette

A detailed vignette is available with the package to demonstrate the use of each 
of the functions.

## Citation

If you use this package, please cite:
```

Citation information
```

## Getting Help

Bug reports and feature requests: https://github.com/yourusername/inferRecom/issues
